---
title: "Combining donor lists"
output: html_notebook
---

## Data preparation

- We are starting with an Excel spreadsheet `data-raw/Donor_History_responsive - no id.xlsx`. It is a list of donations to the University of Texas over a 10-year period, acquired by UT Austin student Carlos Garcia through an open records request.
- The spreadsheet has three sheets: "Part 1", "Part 2" and "Part 3"
- Our goal here is to combine the three sheets into a single CSV file.

### Install package

These are the packages required for this notebook, commented out in case they are already installed.


```{r}
# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("lubridate")
```

### Load necesary packages

```{r}
library(tidyverse)
library(readxl)
library(lubridate)
```

### Import the three sheets as dataframes

```{r}
part1 <- read_excel("data-raw/Donor_History_responsive - no id.xlsx", sheet = "Part 1")
part2 <- read_excel("data-raw/Donor_History_responsive - no id.xlsx", sheet = "Part 2")
part3 <- read_excel("data-raw/Donor_History_responsive - no id.xlsx", sheet = "Part 3")
```

### Merge the three dataframes

```{r}
combined <- rbind(part1, part2, part3) %>% 
  mutate(DONATION_DATE = dmy(DONATION_DATE))
```

### Export as csv

```{r}
combined %>% write_csv("data-done/donors.csv")
```


